%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Computational Algorithms Project Monitor} % Job title
    {CEFET/RJ} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Aug. 2019 - Aug. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assited professor with general tasks.}
        \item {Supported undergraduate students by teaching and explaining C, C++ and Python Languages.}
        \item {Supported undergraduate students by teaching and explaining fundamental data structures, including arrays, matrices, and queues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Discrete Mathematics Monitor} % Job title
    {CEFET/RJ} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Aug. 2020 - Feb. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assited professor with general tasks.}
        \item {Supported undergraduate students by teaching and explaining set theory, functions, graphs and others topics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Bluemoon} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Jun. 2021 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed several Frontend validators for data handled by forms.}
        \item {Designed and developed several forms pages in corporation CRMs using Angular, HTML and SASS with Backend integration.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fullstack Developer} % Job title
    {Bluemoon} % Organization
    {Rio de Janeiro, Brazil} % Location
    {Jul. 2021 - Aug. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a web crawler with on python.}
        \item {Managed database performance and backups.}
        \item {Created migrations and seeds to setup local development.}
        \item {Managed CRMs CI/CD configuration using Heroku, Vercel, AWS and Docker.}
        \item {Designed, developed and deployed several MySQL databases.}
        \item {Designed, developed and deployed several CRONs (scheduled jobs).}
        \item {Designed, developed and deployed several dashboards for the corporation CRMs.}
        \item {Designed, developed and deployed several external API integrations in Backend and Frontend.}
        \item {Designed, developed and deployed several new Backend features using NestJS, Knex.JS, TypeORM, Prisma and MySQL.}
        \item {Designed, developed and deployed CRM integration with corporation communication platforms (Slack, WhatsApp, etc...).}
      \end{cvitems}
    }

    %---------------------------------------------------------
      \cventry
        {Fullstack Developer} % Job title
        {ONErpm} % Organization
        {São Paulo, Brazil} % Location
        {Feb. 2023 - PRESENT} % Date(s)
        {
          \begin{cvitems} % Description(s) of tasks/responsibilities
            \item {Dockerized Backend and Frontend systems.}
            \item {Automated workflows and processes using AI.}
            \item {Refactored and upgraded laravel and angular systems.}
            \item {Created migrations and seeds to setup local development.}
            \item {Optimized complex SQL queries and huge reports generation.}
          \end{cvitems}
        }

%---------------------------------------------------------
\end{cventries}
